resistanceModelNotesAndy

### 2015-07-07 resistanceModelNotesAndy.Rmd
notes

>>>>

** 7/7/15 **
resistanceMaster() does reproduce curtis fig2
so the parameters in system.file("extdata","input.parameters.csv", package="resistance")
must work

what is different about the input params in the sensitivity analysis ?

resistanceMaster() still calls runModel() if I change it to call runModel2() does it still work ??

No I get this :
Error in runModel2(input, calibration) : 
  Error in male exposures: must total one:  1.9

but in the input files, looks like it is -- 0.1 & AB 0.9 for all.

No not in the hardcoded, curtis fig2 input which comes from the program. It has a 0.9 for ab which slips in too.

                                             B (HCH)   A (DDT) Combination
Calibration (100 default)                  1012.0000 1012.0000   1.012e+03
Number of generations                        70.0000   70.0000   1.600e+02
Collect fitness scores in matrix (1/0)        1.0000    1.0000   1.000e+00
Export fitness scores matrix to .csv (1/0)    0.0000    0.0000   0.000e+00
Frequency of R at locus 1                     0.0100    0.0100   1.000e-02
Frequency of R at locus 2                     0.0100    0.0100   1.000e-02
Recombination Rate                            0.5000    0.5000   5.000e-01
Exposure Males -,-                            0.1000    0.1000   1.000e-01
Exposure Males a,-                            0.0000    0.0000   0.000e+00
Exposure Males A,-                            0.0000    0.9000   0.000e+00
Exposure Males -,b                            0.0000    0.0000   0.000e+00
Exposure Males -,B                            0.9000    0.0000   0.000e+00
Exposure males a,b                            0.0000    0.0000   9.000e-01
Exposure Males A,B                            0.0000    0.0000   9.000e-01
...

exactly where is that input object created ?
createInputMatrix()
fixed bug, but it didn't effect the output

can I compare the inputs for the 3 scenarios by Beth to those in my first scenario ? in a csv.

This gets the file to create Curtis Fig2.
```
inputCurtis <- createInputMatrix(FALSE)

Can I paste the input for the first scenario onto it ?
Or might be better just to output all 100 scenarios.

see :

seems that the dominance coefficient of locus2 in -B is much lower in Beths than in the sensi scenarios.

Dominance coefficient L2 in -,B	0.0016	0.0016	0.00016	0.944675269	0.497699242

First see if the curtis fig2 persists when dominance for the mixture is reduced.

Good news that this correction seemed to make the graph closer to Curtis. 
    #input[37,3] <- 0.00016	#Dominance coefficient in B
    #? should this be the same as the value in ,2 & ,1
    input[37,3] <- 0.0016	#Dominance coefficient in B
